TBD

### 2021-03-09 outputs/paper/paper.Rmd
up

```{r fs, fig.width=10, fig.height=10 }
library(randomForest)
library(plyr)

# deal with missing value
FS<- dat%>%
select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt,exp_2_prompt,post_favor_Klobuchar,post_favor_Warren,post_favor_Biden,post_favor_Bloomberg,exp_2,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main))%>%
na.omit()

set.seed(123)
FS_tree<-randomForest(post_favor_Sanders~., data=FS, importance=TRUE,proximity=TRUE)

FS_tree<-as.data.frame(FS_tree$importanceSD)

FS_tree<- FS_tree[order(-FS_tree[,]),,drop=FALSE]
FS_tree<- cbind(Variable_name = rownames(FS_tree), FS_tree)
rownames(FS_tree) <- 1:nrow(FS_tree)
FS_tree<- as.data.frame(FS_tree)
```

```{r tree, echo=FALSE, fig.width=8, fig.height=7}
ggplot(FS_tree, aes(x=FS_tree$Variable_name, y=FS_tree$`FS_tree$importanceSD`)) +
  geom_segment( aes(x=FS_tree$Variable_name,xend=FS_tree$Variable_name, y=0, yend=FS_tree$`FS_tree$importanceSD`), color="grey") +
  geom_point( color="orange", size=4) +
  theme_light() +
  coord_flip()+
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  xlab("") +
  ylab("Value of Y")

@@

>>>>

```{r fs, echo=FALSE, fig.width=10, fig.height=10 }
library(randomForest)
library(plyr)

# deal with missing value
FS<- dat%>%
select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Warren,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake))%>%
na.omit()
## feature selection 
set.seed(123)
FS_tree<-randomForest(post_favor_Sanders~., data=FS, importance=TRUE,proximity=TRUE) ## variable importance

FS_tree<-as.data.frame(FS_tree$importanceSD) # transform to dataframe

FS_tree<- FS_tree[order(-FS_tree[,]),,drop=FALSE] # sort importance by descending order

FS_tree<- cbind(Variable_name = rownames(FS_tree), FS_tree)
rownames(FS_tree) <- 1:nrow(FS_tree)
FS_tree<- as.data.frame(FS_tree)
```

```{r tree, echo=FALSE, warning=FALSE, fig.width=8, fig.height=7}

FS_tree%>%
  mutate(name = fct_reorder(FS_tree$Variable_name,FS_tree$`FS_tree$importanceSD`))%>%
  ggplot(aes(x=FS_tree$Variable_name, y=FS_tree$`FS_tree$importanceSD`)) +
  geom_segment( aes(x=FS_tree$Variable_name,xend=FS_tree$Variable_name, y=0, yend=FS_tree$`FS_tree$importanceSD`), color="grey") +
  geom_point( color="orange", size=4) +
  theme_light() +
  coord_flip()+
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  xlab("") +
  ylab("Importance value")+
  ggtitle("Variable importance plot")

@@

## regression model

```{r regression, echo=FALSE, warning=FALSE, fig.width=8, fig.height=7}

## transfer data into dummy
library(fastDummies)

Dummy_data<- fastDummies::dummy_cols(FS, remove_first_dummy = TRUE, remove_selected_columns = TRUE)%>%
  select(-c(2:4))#  change categorical var to factors

##create model
model <- lm(post_favor_Sanders ~., data =Dummy_data )
summary(model)
```
